The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-01-31 paper/paper.Rmd
fix typos

We assume that speaker effort is related to the suprisal of an utterance in a particular context\footnote{In the current set of simulations we consider utterances costs as independent from context (ie. $p(u|c)p(c)=p(u)p(c)$).} -- intuitively, the number of bits needed to encode the utterance $u$. This particular formalization of speaker-cost is general enough to accommodate a range of cost instantiations, such as production difficult via articulation effort, cognitive effort related to lexical access, or others [@BennettGoodman2015a].\par

@@

We assume listener effort is the semantic suprisal of a meaning given an utterance. This operationalization of listener effort is intuitively related to existing work in sentence processing in which word comprehension difficulty is proportional to surprisal [@Hale2001a; @Levy2008a].

>>>>

We assume that speaker effort is related to the surprisal of an utterance in a particular context\footnote{In the current set of simulations we consider utterances costs as independent from context (ie. $p(u|c)p(c)=p(u)p(c)$).} -- intuitively, the number of bits needed to encode the utterance $u$. This particular formalization of speaker-cost is general enough to accommodate a range of cost instantiations, such as production difficult via articulation effort, cognitive effort related to lexical access, or others [@BennettGoodman2015a].\par

@@

We assume listener effort is the semantic surprisal of a meaning given an utterance. This operationalization of listener effort is intuitively related to existing work in sentence processing in which word comprehension difficulty is proportional to surprisal [@Hale2001a; @Levy2008a].

### 2019-01-31 paper/paper.tex
fix typos

We assume that speaker effort is related to the suprisal of an utterance
in a particular
context\footnote{In the current set of simulations we consider utterances costs as independent from context (ie. $p(u|c)p(c)=p(u)p(c)$).}
-- intuitively, the number of bits needed to encode the utterance \(u\).
This particular formalization of speaker-cost is general enough to
accommodate a range of cost instantiations, such as production difficult
via articulation effort, cognitive effort related to lexical access, or
others (Bennett \& Goodman, 2018).\par

@@

We assume listener effort is the semantic suprisal of a meaning given an
utterance. This operationalization of listener effort is intuitively
related to existing work in sentence processing in which word
comprehension difficulty is proportional to surprisal (Hale, 2001; Levy,
2008).

>>>>

We assume that speaker effort is related to the surprisal of an
utterance in a particular
context\footnote{In the current set of simulations we consider utterances costs as independent from context (ie. $p(u|c)p(c)=p(u)p(c)$).}
-- intuitively, the number of bits needed to encode the utterance \(u\).
This particular formalization of speaker-cost is general enough to
accommodate a range of cost instantiations, such as production difficult
via articulation effort, cognitive effort related to lexical access, or
others (Bennett \& Goodman, 2018).\par

@@

We assume listener effort is the semantic surprisal of a meaning given
an utterance. This operationalization of listener effort is intuitively
related to existing work in sentence processing in which word
comprehension difficulty is proportional to surprisal (Hale, 2001; Levy,
2008).
